Time Series Length at Which Block Bootstrapping is Effective for Estimation of Variance

### 2022-09-22 Manuscript/manuscript.tex
Update
References

@@

In this experiment, there are certain factors that are expected to affect the coverage
rates. As the Auto-Regressive (AR) coefficient (the time dependence) of the time series increases,
we expect the coverage rates of the confidence intervals to decrease.
The coverage rates are also affected by the size of the blocks - more specifically,
how the size of the blocks (l) relates to the size of the time series (n) - 
and whether or not they overlap.

@@

@@

For the simulations using a constant block length of 10, the sample size was gradually lowered by increments of 20 to see when
the block bootstrap would begin to consistently return coverage rates below .90. For AR = 0.2 using a constant l, results for
sample sizes ranging from 400 to 20 were observed. For AR = 0.4 using a constant l, results for sample sizes ranging from 600
to 20 were observed. For AR = 0.6, using a constant l, results for sample sizes ranging from 900 to 220 were observed. For the simulations in which the block length was the square root of the time series length, the only sample sizes used were perfect squares so that the blocks would have whole number lengths. For AR = 0.2 using l = sqrt{n}, results for sample sizes ranging from 625 to 36 were observed. For AR = 0.4 using sqrt{n}, results for sample sizes ranging from 900 to 121 were observed. For AR = 0.6 using l = sqrt{n}, results for sample sizes ranging from 1600 to 121 were observed.

\section{Results}

As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was required for effective block bootstrap estimation.

\begin{figure}[]
  \centering
  \includegraphics[width=\textwidth]{constant_0.2}
  \caption{}
  \label{fig:constant_0.2}
\end{figure}

>>>>

Block bootstrapping is a widely used method in Statistics. The concept for block 
bootstrapping was developed independently by. It has been applied to a variety of 
different fields such 
as econometrics \citep{MacKinnon} and meteorology \citep{Varga}. It can be used for 
situations in which there is temporal dependence and the goal is estimation or hypothesis 
testing. It is useful for a variety of applicationsAssuming that the sample is infinitely 
large, the method will work perfectly. However, for a finite sample size, the method will 
not work as well as expected. It may be necessary (in order to plan an applied 
statistical 
procedure) to know at which sample size the method stops working at an acceptable level. 
The goal of this study is to find a threshold or range of sample sizes at block bootstrap 
is no longer an effective method for estimating variance.

\citet{Nevitt} find that a sample size of 200-1000 is usually sufficient for standard 
bootstrap estimation. However, block bootstrapping is a different situation especially in 
the context of time series because the sample is split into blocks and there is a time 
dependence factor.

@@

In this experiment, there are certain factors that are expected to affect the coverage
rates. As the Auto-Regressive (AR) coefficient (the time dependence) of the time series 
increases,
we expect the coverage rates of the confidence intervals to decrease.
The coverage rates are also affected by the size of the blocks - more specifically,
how the size of the blocks (l) relates to the size of the time series (n) - 
and whether or not they overlap. It is known that as the size of the time series 
increases, the optimal block length should increase, and the ratio of the block length to 
the time series length should decrease. l = (n)(1/3) is typically considered the optimal 
block length according to asymptotic theory. If only perfect cubes are used for the time 
series length, n gets too large when l increases by relatively little. An alternative 
would be to use smaller time series, find the cube root, and set the block length to the 
nearest whole number. However, in this study l = sqrt{n} is used, as it allows for smaller 
sample sizes, but it still follows the aforementioned principle.

@@

Before each simulation, the random seed was set to 5 so that the randomized results can be 
reproduced.

@@

For the simulations using a constant block length of 10, the sample size was gradually 
lowered by increments of 20 to see when
the block bootstrap would begin to consistently return low coverage rates. For AR = 0.2 
using a constant l, results for
sample sizes ranging from 400 to 20 were observed. For AR = 0.4 using a constant l, 
results for sample sizes ranging from 600
to 20 were observed. For AR = 0.6, using a constant l, results for sample sizes ranging 
from 900 to 220 were observed. For the simulations in which the block length was the 
square root of the time series length, the only sample sizes used were perfect squares so 
that the blocks would have whole number lengths. For AR = 0.2 using l = sqrt{n}, results 
for sample sizes ranging from 625 to 36 were observed. For AR = 0.4 using sqrt{n}, results 
for sample sizes ranging from 900 to 121 were observed. For AR = 0.6 using l = sqrt{n}, 
results for sample sizes ranging from 1600 to 121 were observed.

\section{Results}
\label{sec:results}

As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was 
required for effective block bootstrap estimation. With l = sqrt{n} and AR = 0.2, all 
observed coverage rates were lower than .92 for n <= 144. For all n's <= 49, all observed 
coverage rates were below .90. A coverage rate of .895 was recorded for the non-moving 
method when n = 196, indicating that even at such a sample size, a coverage rate below .90 
is possible. A coverage rate below .90 (.895) was recorded for the moving method at a 
sample size as large as n = 144. With l = sqrt{n} and AR = 0.4, all observed coverage 
rates were below .91 for n <= 169. For all n's <= 100, all observed coverage rates were 
below .90. A coverage rate of .897 was recorded for the non-moving method when n = 400, 
indicating that even at such a sample size, a coverage rate below .90 is possible. A 
coverage rate below .90 (.897) was recorded for the moving method at a sample size as 
large as n = 169. With l = sqrt{n} and AR = 0.6, all observed coverage rates were below 
.91 for n <= 361. For all n's <= 225, all observed coverage rates were below .90. A 
coverage rate of .896 was recorded for the moving method when n = 361, indicating that 
even at such a sample size, a coverage rate below .90 is possible. A coverage rate below 
.90 (.891) was recorded for the non-moving method at a sample size as large as n = 225.

With a constant l and AR = 0.2, for n <= 180, all observed coverage rates were below .92. 
For all n's <= 100, all observed coverage rates were below .90. A coverage rate of .899 
was recorded for the non-moving method when n = 140, indicating that even at such a sample 
size, a coverage rate below .90 is possible. A coverage rate below .90 (.899) was recorded 
for the moving method at a sample size as large as n = 100. With a constant l and AR = 
0.4, for n <= 280, all observed coverage rates were below .92. For all n's <= 120, all 
observed coverage rates were below .90. A coverage rate of .892 was recorded for the 
moving method when n = 260, indicating that even at such a sample size, a coverage rate 
below .90 is possible. A coverage rate below .90 (.896) was recorded for the non-moving 
method at a sample size as large as n = 160. With a constant l and AR = 0.6.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{constant_0.2}
  \caption{}
  \label{fig:constant_0.2}
\end{figure}
